Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-08 paper/paper.Rmd
Minor edits

author-note:
    "*These authors contributed equally. **Project contributors included Carolyn Au, Juan Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampien, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, Jed Tan. Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."

@@

Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication. Our three-point rating system was based on the theoretical interpretation of the original finding, with 0\% = no support for the original interpretation, 50\% = some support for the original interpretation, 100\% = full replication). We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.  The average rating given by instructors and students was `r round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)` and `r round(mean(d$replicated_student, na.rm=TRUE), digits = 2)` respectively.

@@

The distribution of ratings are given in Table \ref{tab:results}, along with breakdowns by various factors of interest. Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons). Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original: `r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
vs. 
`r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%.
There were small numerical effects of being run on Mechanical Turk (`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\% vs. `r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%) and having open materials (`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\% 
vs. `r 100 *round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`\%), though we do not believe these differences are interpretable given our sample size.

>>>>

author-note:
    "*These authors contributed equally. **Project contributors included Carolyn Au, Juan Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampien, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan. Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."

@@

100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%

Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication. Our three-point rating system was based on the theoretical interpretation of the original finding, with 0\% = no support for the original interpretation, 50\% = some support for the original interpretation, 100\% = full replication). We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.  The average rating given by instructors and students was `r 100 * round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)`\% and `r 100 * round(mean(d$replicated_student, na.rm=TRUE), digits = 2)`\% respectively.

@@

The distribution of ratings are given in Table \ref{tab:results}, along with breakdowns by various factors of interest. Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons). Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original (`r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
vs. 
`r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%).
There were small numerical effects of being run on Mechanical Turk (`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\% vs. `r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%) and having open materials (`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\% 
vs. `r 100 *round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`\%), though we do not believe these differences are interpretable given our sample size.
